---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mtab

<!-- badges: start -->
<!-- badges: end -->

The goal of mtab is to help create data structures from regression models which can be used to create publication ready tables.

## Installation

You can install the development version of mtab from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("conig/mtab")
```

## Example

This is a basic example which shows you how to create a hierarchical regression table using {mtab}:

```{r}
library(mtab)

T <- data.frame(datasets::Titanic) |> 
  tidyr::pivot_wider(values_from = "Freq", names_from = "Survived")

T

m1 <- glm(cbind(Yes, No) ~ Sex, data = T, family = "binomial")
m2 <- glm(cbind(Yes, No) ~ Sex + Class, data = T, family = "binomial")
m3 <- glm(cbind(Yes, No) ~ Sex * Class, data = T, family = "binomial")
m4 <- glm(cbind(Yes, No) ~ Sex * Class + Age, data = T, family = "binomial")
tabby <- h_tab(m1, m2, m3, m4)
```

```{r echo = FALSE}
tabby$Term[attr(tabby, "indent")[[1]]] <- paste0("   ", tabby$Term[attr(tabby, "indent")[[1]]])
tabby$Term[!attr(tabby, "indent")[[1]]] <- paste0("**", tabby$Term[!attr(tabby, "indent")[[1]]], "**")
```

Tables can be formatted with a range of functions including kable() or papaja::apa_table

```{r}
tabby |> 
   knitr::kable(escape = FALSE)
```

